### 2018-07-10 pilot_manuscript.Rmd
updates and first try at Results

```{r data-cleanup, eval=FALSE, include=FALSE}
##pull in the data
master = read.csv("overalldata.csv", stringsAsFactors = F)

@@

```{r fix-MFD, eval=FALSE, include=FALSE}
##figure out the percent of MFD words

@@

```{r process-text, eval=FALSE, include=FALSE}
##load libraries
library(tm)
library(ngram)

@@

####random intercept only model####
##note we switched to LME function
model2 = lme(percent ~ 1, 
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno) #sets random intercept for each participant
summary(model2) #note changed Value in output; also, 
#Random effects tells how much intercept varies among Pps
anova(model1, model2) #tests if necessary to nest; Yes, we need to do MLM

####predictor model####
model3 = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno)
summary(model3)
anova(model1, model2, model3)
r.squaredGLMM(model3) #gives you two, report both

model3.1 = lme(percent ~ lean + moraltype, #now we want to switch the 1 for IV of interest
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno)
summary(model3.1)

model3.2 = lme(percent ~ lean * moraltype, #now we want to switch the 1 for IV of interest
               data = long_mlm, 
               method = "ML", 
               na.action = "na.omit",
               random = ~1|partno)
summary(model3.2)

@@

# Results
NUMBERS!!!
# Discussion
How it turned out
What to do for future project
Argue: why is still a good thing to study??

>>>>

```{r data-cleanup, eval=TRUE, include=FALSE}
##pull in the data
master = read.csv("overalldata.csv", stringsAsFactors = F)

@@

```{r fix-MFD, eval=TRUE, include=FALSE}
##figure out the percent of MFD words

@@

```{r process-text, eval=TRUE, include=FALSE}
##load libraries
library(tm)
library(ngram)

@@

####random intercept only model####
##note we switched to LME function
model2 = lme(percent ~ 1, 
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno) #sets random intercept for each participant
summary(model2) #note changed Value in output; also, 
#Random effects tells how much intercept varies among Pps
anova(model1, model2) #tests if necessary to nest; Yes, we need to do MLM
r.squaredGLMM(model2)
####predictor model####
model3 = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno)
summary(model3)
anova(model1, model2, model3)
r.squaredGLMM(model3) #gives you two, report both

model3.1 = lme(percent ~ lean + moraltype, #now we want to switch the 1 for IV of interest
             data = long_mlm, 
summary(model3.1)
r.squaredGLMM(model3.1)
model3.2 = lme(percent ~ lean * moraltype, #now we want to switch the 1 for IV of interest
               data = long_mlm, 
summary(model3.2)
r.squaredGLMM(model3.2)

@@

```{r mlm table}
##three models
table = matrix(NA, nrow = 5, ncol = 10)
colnames(table) = c("Model", "Degrees of Freedom", "AIC", "BIC", 
                    "Log Likelihood", "R2m", "R2c", "Test", "L Ratio", "p-value")

##stick in the information you need
table[1, ] = c("Model 1", 2, 43610.91, 
               43627.55, -21803.46, "", "",
               "", "", "")

table[2, ] = c("Model 2", 3, 43611.04, 
               43636.01, -21802.52, 0.000, 0.004,
               "Model 1 vs Model 2", 1.871644, 0.173)

table[3, ] = c("Model 3", 4, 43604.33, 
               43637.62, -21798.17, 0.0003, 0.0037,
               "Model 2 vs. Model 3", 8.703020, 0.0032)

table[4, ] = c("Model 3.1", 13, 37913.11, 
               38021.30, -18943.55, 0.17, 0.19,
               "Model 3 vs. Model 3.1", 5709.23, "< .001")

table[5, ] = c("Model 3.2", 22, 37904.00, 
              38087.09, -18930.00, 0.17, 0.19,
               "Model 3.1 vs. Model 3.2", 27.11, 0.001)

##print that sucker out
library(knitr)
kable(table)
```

# Results
Anymore screening/data prep here?

Political lean of the news organization was used to predict the percent of words matching the Moral Foundations Dictionary. According to an analysis of variance (ANOVA) between the intercept-only model (Model 1) and the random intercept-only model (Model 2, *R2m* = 0.00, *R2c* = 0.004), there were no statistically significant differences (*F* = *?*, *p* = 0.17). There was a signficant difference between the random intercept-only model and the predictor model (Model 3, *R2m* = 0.0003, *R2c* = 0.0037), *F* = *?*, *p* = .003).  We found a significant difference between the two political leans (*b* = -0.018, *SE* = 0.006, *t*(3039) = -2.95, *p* = 0.003). Next, we added Moral Foundation Type as a predictor of percent to the third model (Model 3.1, *R2m* = 0.17, *R2c* = 0.19). The ANOVA revealed a significant difference between Models 3 and 3.1, *F* = *?*, *p* < .001)

#Significance for, like, all of the little moral types. Put in table?

Finally, we analyzed the interaction between political lean and Moral Foundation type as a preditor of percent (Model 3.2, *R2m* = 0.17, *R2c* = 0.19). Using ANOVA, we found a significant difference between Models 3.1 and 3.2, *F* = *?*, *p* = .001).

#Again, lots of stuff here. Needs to be reported? Put in table?

Comparisons between the models can be found in Table 1. 
# Discussion
How it turned out
What to do for future project
Argue: why is still a good thing to study??
